Examining Whether Approximate Visualizations Impact Perception of Corrected Visualizations

### 2016-12-08 paper/paper.tex
Regression tables and figures in paper

% for Computer Society papers, we must declare the abstract and index terms
% PRIOR to the title within the \IEEEtitleabstractindextext IEEEtran
% command as these need to go into the title area created by \maketitle.
% As a general rule, do not put math, special symbols or citations
% in the abstract or keywords.
\IEEEtitleabstractindextext{%
\begin{abstract}
The abstract goes here.
\end{abstract}

@@

For question (3), the answers were calculated via a Jaccard Index.

@@

\begin{table}[!t]
% increase table row spacing, adjust to taste
\renewcommand{\arraystretch}{1.3}
% if using array.sty, it might be a good idea to tweak the value of
% \extrarowheight as needed to properly center the text within the cells
\caption{Regression table for Question 1. Baseline is only the precise visualization.}
\label{table_example}
\centering
\begin{tabular}{|c||c|c|c|c|}
\hline
Study parameter & Est. & SE & t & p\\
\hline
\hline
Expected Bias & & & & \\
\hline
Control condition & & & & \\
\hline
Condition:Difference & & & & \\
\hline
Condition:Both & & & & \\
\hline
Expected Bias * Condition:Difference & & & & \\
\hline
Expected Bias * Condition:Both & & & & \\
\hline
\end{tabular}
\end{table}

\begin{figure}[!t]
  \centering
  \includegraphics[width=\columnwidth]{blankheatmap.png}
  \caption{Example heatmap to demonstrate interaction}
  \label{fig:blank_heatmap}
\end{figure}

We will analyze our data through regressions.
For questions with categorical responses, we will use a factorial logistic regression (\texttt{glm} with a \texttt{binomial} family in R).
We will use a factorial ANOVA (\texttt{anova} on \texttt{lm} in R) for questions with interval responses.
Table \ref{table_example} shows what we expect our regression tables to show.

We will likely have to conduct post-hoc Tukey tests to differentiate between study conditions.
We will present the results of those tests graphically.
For example, Figure \ref{fig:blank_heatmap} shows how we will present the amount of bias present in different study conditions for numerical questions, such as question 3 above.

>>>>

% for Computer Society papers, we must declare the abstract and index terms
% PRIOR to the title within the \IEEEtitleabstractindextext IEEEtran
% command as these need to go into the title area created by \maketitle.
% As a general rule, do not put math, special symbols or citations
% in the abstract or keywords.
\IEEEtitleabstractindextext{%
\begin{abstract}
\todo{The abstract goes here.}
\end{abstract}

@@

For question (3), the answers were calculated via a Jaccard Difference between the airlines or states in the visualization and the airlines or states in the participant's answer.

\subsection{Participants}

\todo{Summary demographics about our participants, who we dropped, etc.}

@@

The regression tables of our three types of questions are in tables \ref{table_q1}, \ref{table_q2}, and \ref{table_q3}.
The raw data for our three types of questions are in figures \ref{figure_q1}, \ref{figure_q2}, and \ref{figure_q3}.
We now answer our research questions in turn.

\begin{table}[!t]
% increase table row spacing, adjust to taste
\renewcommand{\arraystretch}{1.3}
% if using array.sty, it might be a good idea to tweak the value of
% \extrarowheight as needed to properly center the text within the cells
\caption{Regression table for question type 1, how many flights were there on an airline or state. Baseline is no difference between the approximate and precise visualization, showing only the precise data in the precise visualization.}
\label{table_q1}
\centering
\begin{tabular}{|l||r|r|r|r@{}l|}
\hline
Study parameter & Est. & SE & t & p & \\
\hline
\hline
Intercept & -0.186 & 0.117 & -1.590 & 0.1160 &  \\
\hline
Approx$\neq$Precise & 0.248 & 0.097 & 2.550 & 0.0128 & * \\
\hline
Expected Bias & -0.126 & 0.463 & -0.271 & 0.7868 &  \\
\hline
VisType\textsubscript{Diff} & -0.112 & 0.096 & -1.167 & 0.2471 &  \\
\hline
VisType\textsubscript{Both} & 0.026 & 0.102 & 0.258 & 0.7970 &  \\
\hline
Expected Bias*VisType\textsubscript{Diff} & 0.234 & 0.522 & 0.449 & 0.6545 &  \\
\hline
Expected Bias*VisType\textsubscript{Both} & 1.037 & 0.583 & 1.778 & 0.0794 & . \\
\hline
\end{tabular}
\end{table}

\begin{table}[!t]
% increase table row spacing, adjust to taste
\renewcommand{\arraystretch}{1.3}
% if using array.sty, it might be a good idea to tweak the value of
% \extrarowheight as needed to properly center the text within the cells
\caption{Regression table for question type 2, comparing how many flights to another airline or state. Baseline is the same as question type 1.}
\label{table_q2}
\centering
\begin{tabular}{|l||r|r|r|r@{}l|}
\hline
Study parameter & Est. & SE & t & p & \\
\hline
\hline
Intercept & 0.395 & 1.156 & 0.342 & 0.7330 &  \\
\hline
Approx$\neq$Precise & -1.101 & 0.926 & -1.189 & 0.2358 & \\
\hline
Expected Bias & 5.961 & 1.674 & 3.560 & 0.0004 & *** \\
\hline
VisType\textsubscript{Diff} & -1.320 & 0.950 & -1.389 & 0.1661 &  \\
\hline
VisType\textsubscript{Both} & -0.590 & 1.018 & -0.580 & 0.5626 &  \\
\hline
Expected Bias*VisType\textsubscript{Diff} & -2.197 & 1.850 & -1.187 & 0.2362 &  \\
\hline
Expected Bias*VisType\textsubscript{Both} & -2.897 & 1.862 & -1.556 & 0.1210 &  \\
\hline
\end{tabular}
\end{table}

\begin{table}[!t]
% increase table row spacing, adjust to taste
\renewcommand{\arraystretch}{1.3}
% if using array.sty, it might be a good idea to tweak the value of
% \extrarowheight as needed to properly center the text within the cells
\caption{Regression table for question type 3, which airlines or states were in the dataset. Baseline is the same as question type 1.}
\label{table_q3}
\centering
\begin{tabular}{|l||r|r|r|r@{}l|}
\hline
Study parameter & Est. & SE & t & p & \\
\hline
\hline
Intercept & 0.146 & 0.128 & 1.139 & 0.2585 &  \\
\hline
Approx$\neq$Precise & -0.009 & 0.026 & -0.334 & 0.7392 & \\
\hline
Expected Bias & 0.826 & 0.148 & 5.578 & $<$0.0001 & *** \\
\hline
VisType\textsubscript{Diff} & 0.294 & 0.157 & 1.866 & 0.0659 &  \\
\hline
VisType\textsubscript{Both} & -0.033 & 0.156 & -0.213 & 0.8318 &  \\
\hline
Expected Bias*VisType\textsubscript{Diff} & -0.335 & 0.181 & -1.853 & 0.0679 & . \\
\hline
Expected Bias*VisType\textsubscript{Both} & 0.045 & 0.183 & 0.247 & 0.8058 &  \\
\hline
\end{tabular}
\end{table}

\begin{figure}[!t]
  \centering
  \includegraphics[width=\columnwidth]{how_many_precise.pdf}
  \caption{Participant data for quesstion type 1 plotted by measured and expected bias.}
  \label{figure_q1}
\end{figure}

\begin{figure}[!t]
  \centering
  \includegraphics[width=\columnwidth]{compare_precise.pdf}
  \caption{Participant data for question type 2 plotted by measured and expected bias.}
  \label{figure_q2}
\end{figure}

\begin{figure}[!t]
  \centering
  \includegraphics[width=\columnwidth]{jaccard_precise_jitter.pdf}
  \caption{Participant data for question type 3 plotted by measured and expected bias.}
  \label{figure_q3}
\end{figure}

\subsubsection{RQ1: Is there a bias?}

\subsubsection{RQ2: Does visualization type impact the bias?}
